Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2016-03-15 tese1/11_related_work_collaboration.tex
[ADD] together JS more info

	\emph{Jitsi Video Bridge} \footnote{\url{http://jitsi.org/Projects/JitsiVideobridge}(accessed June 2, 2015).} receives one stream from every participant on a conference, either from a \emph{jitsi} client or a \ac{WebRTC} application, and redirects it to all the other conference participants, reducing the amount of data that each peer sends. Although all the participants still need to download all the streams from the \emph{Jitsi Video Bridge} server, typically download rates are much bigger than upload rates, making this solution more feasible.
	\emph{Jitsi Video Bridge} uses \ac{XMPP} as a signaling protocol and its \emph{colibri} extension \cite{xep0340} to reserve channels for video transmission. Despite this choice for signaling protocol, \emph{Jitsi Video Bridge} also supports \ac{SIP}.

@@

	\emph{TogetherJS}\footnote{\url{http://togetherjs.com/}(accessed June 2, 2015).} is a JavaScript library that uses \ac{WebRTC} for collaborative web applications. It uses \ac{JSON} messages for \ac{OT} concurrency control but it does not provide storage. {\color{blue}\emph{TogetherJS} uses its own servers for the signaling phase and it supports microphone and mouse sharing between users.}

@@

{\color{green} \emph{TogetherJS} requires a simple server (also known as hub) that echoes messages between clients, all the synchronization work is performed by the clients. Altough the hub's reduced complexity, \emph{TogetherJS}'s server is implemented with \emph{NodeJS}, we would need read the hub's source code and understand what changes are needed to perform on our web server in order to make it compatible with \emph{TogetherJS}.}

>>>>

	\emph{Jitsi Video Bridge} \footnote{\url{http://jitsi.org/Projects/JitsiVideobridge}(accessed June 2, 2015).} receives one stream from every participant on a conference, either from a \emph{jitsi} client or a \emph{WebRTC} application, and redirects it to all the other conference participants, reducing the amount of data that each peer sends. Although all the participants still need to download all the streams from the \emph{Jitsi Video Bridge} server, typically download rates are much bigger than upload rates, making this solution more feasible.
	\emph{Jitsi Video Bridge} uses \ac{XMPP} as a signaling protocol and its \emph{colibri} extension \cite{xep0340} to reserve channels for video transmission. Despite this choice for signaling protocol, \emph{Jitsi Video Bridge} also supports \ac{SIP}.

	{\color{blue}
	\ac{KMS} supports transcoding, group communications, recording, mixing, broadcasting, aplying filters, image and sound analysis, for example it allows face and qrcode detection. \ac{KMS} functionalites are exposed through \emph{JSON-RPC} over \emph{WebSocket}, there are three clients available: JavaScript Client for web browsers, Java Client for Java EE Servers and JavaScript Cleint for Node.js servers. 
	\ac{KMS} suports streaming over \emph{WebRTC}, \ac{HTTP} and \ac{RTP} endpoints. Another important component of \ac{KMS} is \emph{Kurento Repository} which suports recording and playing directly from \emph{MongoDB}, that is important for providing a scalable media storage. Unlinke \emph{Jitsi Video Bridge}, \ac{KMS} does not enforce a specific signaling protocol.
	}

@@

	\emph{TogetherJS}\footnote{\url{http://togetherjs.com/}(accessed June 2, 2015).} is a JavaScript library that uses \ac{WebRTC} for collaborative web applications. It uses \ac{JSON} messages for \ac{OT} concurrency control but it does not provide storage. {\color{blue}\emph{TogetherJS} uses its own servers for the signaling phase and it supports microphone and mouse sharing between users. It requires a simple server (also known as hub) that echoes messages between clients, all the synchronization work is performed by the clients. Altough the hub's reduced complexity, \emph{TogetherJS}'s server is implemented with \emph{NodeJS}, if we would not choose \emph{NodeJS} for server implementation we would need read the hub's source code and understand what changes are needed to perform on our web server in order to make it compatible with \emph{TogetherJS}.}

@@
